Title: A proof-of-concept study

### 2022-01-20 paper.tex
update

\author[0000-0003-3269-4660]{H.-Y. Karen Yang}
\affiliation{Institute of Astronomy and Department of Physics, National Tsing Hua University, Hsinchu 30013, Taiwan}

@@

  %\begin{figure*}[ht]
  \begin{figure*}
    \subfigure[(Reproduced with permission from R. Blatt, Rev. Mod. Phys. 87, 1419 (2015).\
               Copyright 2015 American Physical Society.)\
               Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps in\
               Galactic coordinates centered on the Galactic center, and the view point .]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__x-ray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay.png}
  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
           Note that the panels on left side are diffuse (i.e. no point-like component)\
           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
  }
  \label{fig__gammaRay}
\end{figure*}

>>>>

\author[0000-0003-3269-4660]{H.-Y. Karen Yang}
\affiliation{Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
\affiliation{Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
\affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}

@@

  %\begin{figure*}[ht]
  \begin{figure*}
    \subfigure[(Reproduced with permission from R. Blatt, Rev. Mod. Phys. 87, 1419 (2015).\
               Copyright 2015 American Physical Society.)\
               Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps in\
               Galactic coordinates centered on the Galactic center, and the view point .]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
           Note that the panels on left side are diffuse (i.e. no point-like component)\
           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
  }
  \label{fig__gammaRay}
\end{figure*}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{The observed (left) and simulated (right) photon flux at 1.7 GeV (top), 13.6 GeV (middle), and 108.6 GeV (bottom).\
           Note that the panels on left side are diffuse (i.e. no point-like component)\
           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
  }
  \label{fig__gammaRay}
\end{figure}
